Indoor Dining Shutdowns Negatively Affect Toronto Restaurants’ Performance and Business Practices

### 2021-02-27 outputs/paper/paper.Rmd
Adjusted Appendix headings

## Survey

@@

```{r survey1, echo = FALSE, message = FALSE, fig.cap = "Screenshot of Google Forms Survey Questions 1-8", out.width="90%"}
knitr::include_graphics("survey/01.png")
```

```{r survey2, echo = FALSE, message = FALSE, fig.cap="Screenshot of Google Forms Survey Questions 9-16", out.width="90%"}
knitr::include_graphics("survey/02.png")
```

@@

## Funding Acknowledgement

@@

## Packages

@@

### General data cleaning and analysis

@@

### Figures

@@

### Tables

@@

### RMarkdown Report

@@

### Other

>>>>

## Survey {-}

@@

```{r survey1, echo = FALSE, message = FALSE, fig.cap = "Screenshot of Google Forms Survey Questions 1-8", out.width="95%"}
knitr::include_graphics("survey/01.png")
```

```{r survey2, echo = FALSE, message = FALSE, fig.cap="Screenshot of Google Forms Survey Questions 9-16", out.width="95%"}
knitr::include_graphics("survey/02.png")
```

@@

## Funding Acknowledgement {-}

@@

## Packages {-}

@@

### General data cleaning and analysis {-}

@@

### Figures {-}

@@

### Tables {-}

@@

### RMarkdown Report {-}

@@

### Other {-}
